%
\documentclass[
12pt, % The default document font size, options: 10pt, 11pt, 12pt
%oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
onehalfspacing, % singlespacing Single line spacing, alternatives: onehalfspacing or doublespacing
%draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
%chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
]{MastersDoctoralThesis} % The class file specifying the document structure

\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters

\usepackage{mathpazo} % Use the Palatino font by default

\usepackage[backend=bibtex,style=numeric,natbib=true, sorting=none]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)

\addbibresource[label=refs]{example.bib} % The filename of the bibliography
\addbibresource[label=ownpubs]{ownpubs.bib} % The filename of the bibliography


\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography

\usepackage{arabxetex}

\usepackage[printonlyused,withpage]{acronym}

\usepackage{algorithmic}

\usepackage{adjustbox}


\usepackage{caption}
\usepackage{subcaption}
% \usepackage{subfig}

%-----------------
%	MARGIN SETTINGS
%-----------------

\geometry{
	paper=a4paper, % Change to letterpaper for US letter
	inner=2.5cm, % Inner margin
	outer=3.8cm, % Outer margin
	bindingoffset=.5cm, % Binding offset
	top=1.5cm, % Top margin
	bottom=1.5cm, % Bottom margin
	%showframe, % Uncomment to show how the type block is set on the page
}

%-----------------
%	THESIS INFORMATION
%-----------------

\thesistitle{Automated detection of COVID-19 cases in digital medical images using deep learning approaches} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{Master of Science} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Mahmoud Z. Fetoh} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

\subject{Information Technology} % Your subject area, this is not currently used anywhere in the template, print it elsewhere with \subjectname
\keywords{ } % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\university{Menofia University} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
\department{Information Technology} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
\group{  } % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
\faculty{Faculty of computers and information} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname

\begin{document}


\frontmatter % Use roman page numbering style (i, ii, iii, iv...) for the pre-content pages

\pagestyle{plain} % Default to the plain heading style until the thesis style is called for the body content


\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
COVID-19 is a severe respiratory tract infections. COVID-19 caused by SARS-CoV-2 can readily spread through a contact with an infected person. Monotonically increasing SARS-CoV-2 infections have not only wasted lives but also severely damaged the financial systems of both developing and developed countries. This high spread rate pressure on the health care systems which rise the need to fast methods for diagnosing this disease. Convolutional Neural Networks (CNN) show a great success for various computer vision tasks. However, CNN is a scale-variant model and computationally expensive. In this Thesis, a novel architectures are proposed for multiscale feature extraction and classification and lightweight architecture for COVID-19 diagnosing. The proposed I which is a lightweight CNN model exploits spatial kernel separability to reduce the number of the training parameters to a large extent and regularize the model to only learns linear kernel. Furthermore, This model uses residual connection and batch normalization extensively to maintain the network stability during the training process and provide the model with the regularization effect to reduce the overfitting. Proposed CNN II learns multiscale features using a pyramid of shared convolution kernels with different atrous rates. This scale invariant CNN uses attention based mechanism that is used to guide and select correct scale for each input. Proposed CNN II is an end-to-end trainable network and exploit a novel augmentation technique, Texture Augmentation, to reduce the overfitting. The lightweight architecture is trained using QaTa-Cov19 benchmark dataset achieving  100\% for accuracy, sensitivity, precision and F1-score with a very low parameter count (150K) compared with the other methods in the literature.  Proposed method II achieved a 0.9929 for $F1-score$ tested on QaTa-Cov19 benchmark dataset with a total of $5,040,571$ trainable parameters.
\end{abstract}

\mainmatter % Begin numeric (1,2,3...) page numbering

\pagestyle{thesis} % Return the page headers back to the "thesis" style

% \include{Chapters/Chapter1_intro.tex}
% \include{Chapters/Chapter2_Backgr.tex} 
% \include{Chapters/Chapter3_Related.tex}
\include{Chapters/Chapter4_proposed.tex} 
\include{Chapters/Chapter4_proposed2.tex} 
\include{Chapters/Chapter5_Experment.tex}
\include{Chapters/Chapter6_Conc.tex}

% \nocite{zaki2021covid} 
% \nocite{zaki2022covid} 
% \printbibheading[heading=bibintoc]
% \printbibliography[keyword={publ}, heading=subbibliography, title={Publications}]
% \printbibliography[title={References}]

% \appendix % Cue to tell LaTeX that the following "chapters" are Appendices

% \include{Chapters/ArabSummery.tex}
% \include{Chapters/ArabAbst.tex}
% \include{Chapters/ArabCV.tex}

% %------------

\end{document}  
